{\bf Practical Concurrency Testing} \\ \normalsize \vspace{1em} \begin{tabular}{c} {\em or: How I Learned to Stop Worrying and Love the Exponential Explosion} \end{tabular}

### 2018-12-03 thesis/intro.tex
assorted minor revs, intro, notes on reading this, etc

\subsubsection{Motivation}

@@

\subsubsection{Contributions}

@@

\subsubsection{Organization}

@@

\subsubsection{Notes on reading this thesis}

@@

Color will be used in figures and graphs to add visual contrast and make the data easier to navigate at a glance,
but only in redundant ways also signaled by symbols.
I have made some effort to choose palettes friendly to color-blindness;
should the reader find contrasts too low anyway,
whether being color-blind or reading a physical copy printed in greyscale,
they may be assured all important distinctions still render in monochrome.
For example, ovals and rectangles typically depict different threads,
and $\dagger$ distinguishes state space estimates from completed verifications.

Pronoun use will vary between more specific and more ambiguous to convey additional nuance.
The singular ``I'' is associated with my own research contributions,
while the royal ``we'' should be taken to include the reader,
such as when surveying background material or related work,
to which the author and reader share more similar relationships.
The impersonal ``the programmer'' will be referred to as she/her
to challenge readers' unconscious bias about gender in computer science,
as well as to highlight her role as the intended user, separate from the underlying research.
%to distinguish her from the thesis audience concerned with the underlying research,
Individual students who participated in the user studies will be given the more inclusive they/them.
Gender-neutral pronouns will also be used on the author themself.

This document is, in a way, only half the work of the thesis, the other half being Landslide's implementation.
While some readers may prefer to be taught in prose and/or mathematical notation how an algorithm works,
others may find that disorienting and wish to see things in a way a compiler would understand.
Chapter~\ref{chap:landslide} provides source code links and serves as a guide to browsing the repository.
Later chapters will often make parenthetical references to specific files and/or functions
therein which implement a feature under discussion.

>>>>

\section{Motivation}

@@

\section{Contributions}

@@

\section{Organization}

@@

\section{Notes on reading this thesis}

\subsubsection{Experience}

@@

\subsubsection{Vision}

Color will be used in figures and graphs to add visual contrast and make the data easier to navigate at a glance,
but only in redundant ways also signaled by symbols.
I have made some effort to choose palettes friendly to color-blindness;
should the reader find contrasts too low anyway,
whether being color-blind or reading a physical copy printed in greyscale,
they may be assured all important distinctions still render in monochrome.
For example, ovals and rectangles typically depict different threads,
and $\dagger$ distinguishes state space estimates from completed verifications.
\revision{Should any vision-impaired reader require fully-textual figure descriptions,
I would be happy to provide them upon request.}

\subsubsection{Language}

Pronoun use will vary between more specific and more ambiguous to convey additional nuance.
The singular ``I'' is associated with my own research contributions,
while the royal ``we'' should be taken to include the reader,
such as when surveying background material or related work,
to which the author and reader share more similar relationships.
The impersonal ``the programmer'' will be referred to as she/her
to challenge readers' unconscious bias about gender in computer science,
as well as to highlight her role as the intended user, separate from the underlying research.
%to distinguish her from the thesis audience concerned with the underlying research,
Gender-neutral pronouns will be used to refer to
individual students who participated in the user studies,
%will be given the more inclusive they/them.
%Gender-neutral pronouns will also be used
as well as
on the author themself.

\subsubsection{Code}

\newcommand\landslidelicense{BSD\xspace}

This document is, in a way, only half the work of the thesis, the other half being Landslide's implementation.
While some readers may prefer to be taught in prose and/or mathematical notation how an algorithm works,
others may find that disorienting and wish to see things in a way a compiler would understand.
\revisionminor{
The Landslide codebase is open-source under the \landslidelicense license,
available at \url{https://github.com/bblum/landslide}.
Chapter~\ref{chap:landslide} provides more detail and}
serves as a guide to browsing the repository.
Later chapters will often make parenthetical references to specific files and/or functions
therein which implement a feature under discussion.

### 2018-12-03 thesis/landslide.tex
update landslide head commit pointer in case i forget later
assorted minor revs, intro, notes on reading this, etc

% TODO: add some backup linkeroos
The Bochs port of Landslide is likewise open-source and available at \url{https://github.com/bblum/landslide}.
% TODO: refresh
The HEAD commit at the time of writing is 5d45e2c.
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.
Development on the Simics port is largely frozen,
as the Bochs port implements all the same features and more,
and is also roughly 3x faster.

@@

\begin{itemize}
	\item {\tt -p PROGRAM}: the name of the test case to invoke
	\item {\tt -t TIME}: wall-clock time limit, in seconds; or suffixed with one of {\tt ydhms} for years, days, hours, minutes, or seconds respectively (default 1h)
	\item {\tt -c CPUS}: maximum number of Landslide instances to run in parallel (defaults to half the number of system CPUs)
	\item {\tt -i INTERVAL}: interval of time between printing progress reports (default 10s)
	\item {\tt -d TRACEDIR}: directory for resulting bug traces (default current directory)
	\item {\tt -v}: verbose mode (issues output for each executed interleaving by each instance of landslide, makes progress reports more detailed, etc)
	\item {\tt -l}: leave Landslide log files from completed state spaces even when no bug was found (deleted automatically by default)
	\item {\tt -h}: print help text and exit immediately
\end{itemize}

>>>>

% TODO: add some backup linkeroos
The Bochs port of Landslide is likewise open-source
\revisionminor{under the \landslidelicense license}
and available at \url{https://github.com/bblum/landslide}.
% TODO: refresh
The HEAD commit at the time of writing is 8127151.
The Simics port uses Simics's proprietary API and is hence unlicensed and available upon request for educational use only.
Development on the Simics port is largely frozen,
as the Bochs port implements all the same features and more,
and is also roughly 3x faster.

@@

\begin{itemize}
	\item {\tt -p PROGRAM}: the name of the test case to invoke
	\item {\tt -t TIME}: wall-clock time limit, in seconds; or suffixed with one of {\tt ydhms} for years, days, hours, minutes, or seconds respectively (default 1h)
	\item {\tt -c CPUS}: maximum number of Landslide instances to run in parallel (defaults to half the number of system CPUs)
	\item {\tt -i INTERVAL}: interval of time between printing progress reports (default 10s)
	\item {\tt -d TRACEDIR}: directory for resulting bug traces (default current directory)
	\item {\tt -v}: verbose mode (issues output for each executed interleaving by each instance of landslide, makes progress reports more detailed, etc)
	\item {\tt -l}: leave Landslide log files from completed state spaces even when no bug was found (deleted automatically by default)
	\item {\tt -h}: print help text and exit immediately
	\item \revision{{\tt -s}: include ``secret'' options when printing help text}
\end{itemize}
